We have to implement the advanced search extension. Here are more details about the way we imagine to improve the search results. We hope that those ideas will encourage users to use the website because it'll give efficient search responses.

% Toutes ces magnifiques idées n'aparaissent ni dans le diagrame de classe ni dans les diagrames de sequence ni dans un quelconque box pointer.....

\subsection{Search by location}
To improve the search efficiency, we think to order results by location. So the nearest services are the firsts to be shown.
With this solution, we add a "local" side at the application, allowing user to create little local sharing communities.
Moreover, by doing that, we think about the ecology and the time spend by the user.
To do this, we think using the google services that allows us to find geographic coordinates giving the database addresses.\\
That explains the fact that organisations and users can have more than one address. Indeed, the user can live near a local address of the organisation but far away of the headquarters. On the user side, maybe a person does regularly a move for his job or to practice his favourite sports. So he can add the one or more address of places where he can offer or demand a service.

\subsection{Filtering with multiple fields}
Like eBay or others buying websites, we want to allow the users to filter the search with multiple fields, like good karma user, nearly ending service, category, etc. Adding filters allow users to find faster the service that he is searching for. He will be able to drop all the services he doesn't need so the response page will the contains less useless informations.

\subsection{Favourite searches}
We want to allow a user to save some search criteria. So, each time he log in, he will be able to make a new search with his chosen criteria.
It will allow him to spend less time in configuration and more time on looking for services. 
This can be easily done via cookies.
