\subsection{Non-functional requirements}
\begin{itemize}

    \item \textbf{Security :} As a \textit{unregistered user}, I want to \textit{sign in in a safe way} in order to \textit{protect my data}. Only password and ID cards data will be encrypted in storage. 

    \item \textbf{Speed :} As a \textit{user}, I want that \textit{the system to respond quickly on my search} in order to \textit{lower waste of time at most}.

    \item \textbf{Modularity :} As an \textit{IT-worker} I want \textit{the system to be modular and commented} in order to \textit{be easy to extend}.

    \item \textbf{Coherence : }  As \textit{a user},I want \textit{all the pages of the website to have the same style} in order to \textit{navigate more easily}.

\end{itemize}
\subsection{Functional requirements}
\begin{itemize}

    \item Create an account for a user or an organisation

    \item Search in the offers/demands list

    \item Add an offer or a demand

    \item Add a user affiliated to an organisation
    
    \item When a user accept an offer, the offer isn't deleted until the user put a reward about the transaction.  With this solution, a user with a transaction that is'nt realized yet can find another user.  In this way, a non achieved transaction doesn't block the user.
    \item Finally, we think that we can add a "Quick add Offer/Demand" system.  When you perform a search, this system can create a perfect demand/offer that match with a result.  With this solution, a user doesn't create manually a demand/offer that correspond exactly of a offer/demand he will.

\end{itemize}
\subsection{UI requirements}
\begin{itemize}

    \item We should keep in mind that some client have a slow connection and don't support last standards. In addition to a mobile version, we should propose a light version of the website.

\end{itemize}