\subsection{The framework}

We have chosen \emph{Ruby on Rails (RoR)} as framework for the project. After some research about existing frameworks, we found that RoR give us many advantages. We have listed these pros here :

\begin{itemize}
   \item RoR constraints us to use the MVC design pattern which we are comfortable with.
   \item RoR forces us to apply good practices like \emph{Don't repeat yourself}.
   \item RoR has conventions over configurations that allow us to waste less time configuring our project and making choices.
   \item RoR has an integrated structure. It allows us to have a clean code through the all project.
   \item RoR make easier to manipulate DB. So, it allows to reuse the same DB throughout all devices and platforms (mobile apps, etc.).
   \item RoR already contains development environment like \emph{production}, \emph{test} and \emph{development}. It makes the deployment easier.
   \item RoR provides protection tools against the most used security attacks. It's important in this case because the platform will contains some confidential informations about the users.
   \item RoR has a large active community of users. Then it is easier to find help and documentation.
   \item There's a lot of offers to host and deploy a RoR project. Moreover some are free to use.
\end{itemize}

In addition, lot of companies are looking for RoR developers. So, we're very interested in learning it.

\subsection{The extensions}

\subsubsection{Advanced search engine}

According to us, the research is the core functionality of this project. With relevant search results, users will spend less time to search and then more time to act. Moreover there will be less fruitless
researches.

\subsubsection{Evaluation of exchanges}

This allows to bring more security in the exchanges and ban bad users. It's also a kind of virtual reward that motivate people to do more and better. It build a system based on trust.

\subsubsection{Internal mailbox system}

The demands and offers will be sent via the internal mailbox system. Thanks to that, it will be easier to send messages to a group or several people. In addition, it allows to not reveal the personal email 
address. It also prevent from spam.

\subsubsection{Presentation of search results}

It allows to filter and sort the search results. It's more user-friendly to display the result with some sort of criteria. It attract the user to look at the results because it's beautiful !